Flare Rates and Rotation Periods of 5700 Stars Younger than 300 Myr

### 2023-11-13 src/tex/ms.tex
angstrom
galex

@@

The Far- and Near-Ultraviolet (FUV/NUV) is another tracer of magnetic activity. Young
stars are known to have excess luminosity in both of these wavelengths \citep{}. We use
archival observations from the \textit{Galaxy Evolution Explorer}
\citep[\textit{GALEX};][]{martin05} to search for trends in FUV/NUV saturation and flare
rate saturation. \textit{GALEX} provides broad FUV photometry from $1350-1750$
and NUV photometry from $1750-2750$. We crossmatch our targets with the \textit{GALEX}
catalog. We follow the sample selection methods outline in \citep{schneider18}. We search
a $10''$ radius around the coordinates of each target in our sample. We include targets with
no bad photometric flags (e.g. \texttt{fuv\_artifact} or \texttt{nuv\_artifact == 0}) as defined
in the catalog. This is recommended by the \textit{GALEX} documentation, as flags could be
assigned due to bright star window reflection, dichroic reflection, detector run proximity,
or bright star ghost. We exclude targets with measured magnitudes brighter than 15, which
marks the saturation limit for both the FUV and NUV photometers \citep{morrissey07}.

@@

\begin{figure}[ht!]
    \script{galex.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/galex.pdf}
        \caption{
            Calculated NUV (left) and FUV (right) GALEX flux for stars in our
            sample. We normalize these values by the J-band flux of the star.
            We find no strong correlation between the NUV/FUV flux and the measured
            flare rate or Rossby number.
            The top row shows GKM stars $<50$~Myr; the bottom row
            shows GKM stars $\geq 50$~Myr. M stars are shown as circles, K stars as
            triangles, and G stars as squares. We note that $f_{NUV}$ traces the
            photosphere of GK stars, and therefore may not be the best comparison
            bandpass when looking for trends in magnetic activity.
        }
        \label{fig:galex}
    \end{centering}
\end{figure}

>>>>

\newcommand{\angstrom}{\mbox{\normalfont\AA}}

@@

The Far- and Near-Ultraviolet (FUV/NUV) is another tracer of magnetic activity. Young
stars are known to have excess luminosity in both of these wavelengths \citep{}. We use
archival observations from the \textit{Galaxy Evolution Explorer}
\citep[\textit{GALEX};][]{martin05} to search for trends in FUV/NUV saturation and flare
rate saturation. \textit{GALEX} provides broad FUV photometry from $1350-1750 \angstrom$
and NUV photometry from $1750-2750 \angstrom$. We crossmatch our targets with the \textit{GALEX}
catalog. We follow the sample selection methods outline in \citep{schneider18}. We search
a $10''$ radius around the coordinates of each target in our sample. We include targets with
no bad photometric flags (e.g. \texttt{fuv\_artifact} or \texttt{nuv\_artifact == 0}) as defined
in the catalog. This is recommended by the \textit{GALEX} documentation, as flags could be
assigned due to bright star window reflection, dichroic reflection, detector run proximity,
or bright star ghost. We exclude targets with measured magnitudes brighter than 15, which
marks the saturation limit for both the FUV and NUV photometers \citep{morrissey07}.

@@

\begin{figure}[ht!]
    \script{galex.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/galex.pdf}
        \caption{
            Calculated FUV (left) and NUV (right) GALEX flux for stars in our
            sample. We normalize these values by the J-band flux of the star.
            We find no strong correlation between the NUV/FUV flux and the measured
            flare rate or Rossby number.
            The top row shows GKM stars $<50$~Myr; the bottom row
            shows GKM stars $\geq 50$~Myr. M stars are shown as circles, K stars as
            triangles, and G stars as squares. We note that $f_{NUV}$ traces the
            photosphere of GK stars, and therefore may not be the best comparison
            bandpass when looking for trends in magnetic activity.
        }
        \label{fig:galex}
    \end{centering}
\end{figure}
